---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# safetensors

<!-- badges: start -->
[![R-CMD-check](https://github.com/mlverse/safetensors/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/mlverse/safetensors/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

safetensors is a pure R implementation of the [safetensors](https://github.com/safetensors/safetensors) file format for both reading and writing.
It currently supports the {torch} and {pjrt} frameworks.

## Installation

safetensors can be installed from CRAN with:

``` r
install.packages("safetensors")
```

The development version of safetensors from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mlverse/safetensors")
```

## Example

Here's an example of writing and reading safetensors files in combination with torch:

```{r}
library(torch)
library(safetensors)

tensors <- list(
  x = torch_randn(10, 10),
  y = torch_ones(10, 10)
)

str(tensors)

tmp <- tempfile()
safe_save_file(tensors, tmp)

tensors <- safe_load_file(tmp, framework = "torch")
str(tensors)
```
